---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Lato:wght@300;700&display=swap');

body {
  font-family: 'Lato', sans-serif;
  background: #e6f2ff;
  color: #002244;
  text-align: center;
}

h1, h2 {
  text-transform: uppercase;
  color: #004080;
}

h1 {
  font-size: 32px;
  border-bottom: 2px solid #66a3ff;
}

p {
  font-size: 18px;
  max-width: 800px;
  margin: auto;
}


```

## An observation of UoA student's weekly walking steps report

**The data collection of a total number in weeks, showing that UoA student's walking highest steps of each week and what exact day is**

**The first plot showing the data of maximum steps per week, which can see that most of the highest steps are on Tuesday**

**The second plot showing the day of week that the highest walking steps is and count it**

```{r}
library(tidyverse)
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSK8rLObAmnEoTyLE56fxVe0dZIgSI72WsHnDIKEY5uhv4FmmJKQ6s2VGrJaIFouK3ivYCX9ktfd43r/pub?gid=1067913358&single=true&output=csv")
lastest_data <- logged_data %>%
  rename(average = `Average walking steps in a week`, 
         max_in_week = `When do you have the most walking steps in a week?`,
         max_steps = `Highest number of  steps in a week`)

max_ste <- max(lastest_data$max_steps)
total <- nrow(lastest_data)
paste("The highest recorded steps in a week is",max_ste, "steps.")
paste("There are",total, "total number of samples so far")

lastest_data %>%
  ggplot() +
  geom_bar(aes(x = max_in_week),
           fill = "#000000")

lastest_data %>%
  ggplot() +
  geom_bar(aes(x = max_steps),
           fill = "#B2C248")


```


